---
title: "Homework 6"
author: "Devin Adams"
date: "1/28/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

## Concepts  

1.  Compare and contrast filter and select.  
Filter is used to select rows (or observations) and select is used to select columns (or variables).  
1.  Explain how ":" can be used when selecting variables.  
":" can be used to columns in a range. For example you can select columns 6,7,8,9, and 10 by using the colon like "6:10". It can also be used with named columns as well such as "arrival_time:dep_delay" selects all the columns from arrival_time to dep_delay.  

## Interpretation of code  

Interpret the following R code:  

```{r code chunk interpretation, warning = FALSE}
converted_times <- mutate(
  flights,
  hours = dep_time %/% 100,
  minutes = dep_time %% 100,
  minutes_after_midnight = 60 * hours + minutes
)
ggplot(
  data = converted_times,
  mapping = aes(x = origin,
                y = minutes_after_midnight,
                fill = origin)
) +
  geom_violin(show.legend = FALSE) +
  geom_boxplot(width = 0.1,
               fill = "grey",
               show.legend = FALSE) +
  coord_flip()
```

Line 25: Declares the following chunk as r code and suprresses any warnings from showing.
Line 26: Creates a new variable called "converted_times" by mutating data
Line 27: Flights is the data that will be mutated with the following calculations. These new columns will be added at the end of the flights data.  
Line 28: A new column is created called "hours" and is calculated by dividing the dep_time by 100 using integer division  
Line 29: A new column is created called "minutes" and is calculated by dividing the dep_time by 100 using  modular division  
Line 30: A new column is created called "minutes_after_midnight" and is calculated by multiplying the hours previously calculated by 60 then adding minutes  
Line 31: Ends the mutate function  
Line 32: Begins a ggplot  
Line 33: The data being used to plot is the converted_times    
Line 34: The origin is mapped to the x axis  
Line 35: The minutes_after_midnight is mapped to the y axis  
Line 36: The origin is mapped to the fill color of the plot  
Line 37: The ggplot function is ended  
Line 38: A violin plot is created and the legend is turned off  
Line 39: A boxplot is created and the width is reduced to 0.1  
Line 40: The fill color of the boxplot is grey  
Line 41: The legend for the boxplot is turned off  
Line 42: The coordinate axes are flipped

## Coding Problem 1:

1.  Select only those flights going from JFK to Chicago.  
1.  Create a data frame that includes the following variables: dep_delay and arr_delay.    
1.  Rename the variables dep_delay to departure and arr_delay to arrival.  
1.  Draw a scatterplot of arrival on departure with colored loess and linear regression smoothers without confidence intervals.  


```{r JFK to Chicago}

```  

## Coding Problem 2: Use mutate and the ranking function to find the 5 most delayed flights departing from JFK.
1.  Choose the flights departing from JFK
1.  Create a new variable called delay which is the rank of the delay with 1 being the longest delay.
1.  For the five most delayed flights, print the new variable delay along with year, month, day, dest, carrier, and dep_delay with the most delayed at the top of the table.  

```{r 5 most delayed flights}

```  

